On Secure Delegation of SampBQP with a Classical Client

### 2020-03-22 qpip.tex
Fix typo

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
	Pick $\varepsilon=\poly(T^{-1})$
	Let $C'$ be $C$ padded with $\poly(\varepsilon^{-1})$ identity gates at the end.
	Pick $h=\poly(\varepsilon)$, $m=O(h^{-3})$, $M=\poly(m)$.

@@

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $O(T^-\lambda)$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$, $\delta=2h$ to get
	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$

>>>>

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$}\label{ProtoQPIP1}
	Pick $\varepsilon=\poly(T^{-1})$.
	Let $C'$ be $C$ padded with $\poly(\varepsilon^{-1})$ identity gates at the end.
	Pick $h=\poly(\varepsilon)$, $m=O(h^{-3})$, $M=\poly(m)$.

@@

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $O(\poly(\varepsilon))$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$, $\delta=2h$ to get
	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
